---
title: "reproducible-research-checklist"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### DO: Start with Good Science  
- Garbage in, garbage out  
- Coherent, focused question simplifies many problems  
- Working with good collaborators reinforces good practices  
- Something that's interesting to you will (hopefully) motivate good habits  

### DON'T: Do Things By Hand
- Editing spreadsheets of data to "clean it up"  
    - Removing outliers  
    - QA / QC  
    - Validating  
- Editing tables or figures (e.g., rounding, formatting)  
- Downloading data from a website (clicking links in a web browser)  
- Moving data around your computer; splitting / reformatting data files  
- "We're just going to do this once..."  

Things done by hand need to be precisely documented (this is harder than it sounds)

### DON'T: Point and Click
- Many data processing/statistical analysis packages have graphical user interfaces (GUIs)  
- GUIs are convenient/intuitive but the actions you take with a GUI can be difficult for others to reproduce  
- Some GUIs produce a log file or script which includes equivalent commands; these can be saved for later examination  
- In general, be careful with data analysis software that is highly *interactive*; ease of use can sometimes lead to non-reproducible analyses  
- Other interactive software, such as text editors, are usually fine  

### DO: Teach a Computer
- If something needs to be done as part of your analysis/investigation, try to teach your computer to do it (even if you only need to do it once)  
- In order to give your computer instructions, you need to write down exactly what you mean to do and how it should be done  
- Teaching a computer almost guarantees reproducibility  

For example, by hand, you can  
1.  Go to the UCI Machine Learning Repository at [http://archive.ics.uci.edu/ml](http://archive.ics.uci.edu/ml)  
2.  Download the [Bike Sharing Dataset]() by clicking on the link to the Data Folder, then clicking on the link to the zip file of the dataset, and choosing "Save Linked File As..." and then saving it to a folder on the computer  

Or you can teach a computer to do the same thing using R:

```
download.file("http://archive.ics.uci.edu/ml/machine-learning-databases/00275/Bike-Sharing-Dataset.zip", "ProjectData/Bike-Sharing-Dataset.zip")
```

Notice here that  
- The full URL to the dataset is specified (no clicking through a series of links)  
- The name of the file saved to your local computer is specified  
- The directory in which the file was saved is specified ("ProjectData")  
- Code can always be executed in R (as long as link is available)

### DO: Use Some Version Control
- Slow things down  
- Add changes in small chunks (don't just do one massive commit)  
- Track/tag snapshots; revert to old versions  
- Sofware like GitHub/BitBucket/SourceForge make it easy to publish results

### DO Keep Track of Your Software Environment
- If you work on a complex project involving may tools/datasets, the software and computing environment can be critical for reproducing your analysis  
- **Computer architecture**: CPU (Inte, AMD, ARM), GPUs  
- **Operating system**: Windows, Mac OS, Linux/Unix
- **Sofware toolchain**: compilers, interpreters, command shell, programming languages (C, Perl, Python, etc.), database backends, data analysis software  
- **Supporting software/infrastructure**: Libraries, R packages, dependencies  
- **External dependencies**: Web sites, data repos, remote databases, sofwtare repos  
- **Version numbers**: Ideally, for everything (if available)

```{r}
sessionInfo()
```

